TBD

### 2016-10-19 paper.tex
LINCAL sort of complete

\section{LINCAL}
%Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
We can rewrite Eq.~\eqref{eq:vis_red_vec} to
\begin{equation}
\label{eq:lincal_vec}
\bd = \bv(\bvarrho) + \bn, 
\end{equation}
where 
\begin{align}
\left [ \bv(\bvarrho) \right ]_{\alpha_{pq}} &= e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q}\\
&= v_{pq},
\end{align}
and
\begin{equation}
\bvarrho = 
\begin{bmatrix}
\bmath{\eta} \\
\bvarphi \\
\widetilde{\bmath{\eta}} \\
\widetilde{\bvarphi}
\end{bmatrix},\qquad
\begin{aligned}
\bmath{\eta} &= [\eta_1, \eta_2,\cdots \eta_N]^T\\
 \bmath{\varphi} &= [\varphi_1, \varphi_2,\cdots \varphi_N]^T\\
 \widetilde{\bmath{\eta}} &= [\widetilde{\eta_1}, \widetilde{\eta_2},\cdots \widetilde{\eta_L}]^T\\
 \widetilde{\bmath{\varphi}} &= [\widetilde{\varphi_1}, \widetilde{\varphi_2},\cdots \widetilde{\varphi_L}]^T
\end{aligned}.
\label{eq:help}
\end{equation}
Note that the vectors $\bmath{\eta},~\bvarphi,~\widetilde{\bmath{\eta}}$ and $\widetilde{\bvarphi}$ are real valued.

The first oreder Taylor expansion of Eq.~\eqref{eq:lincal_vec} around the fiducial point $\bvarrho_0$ is equal to
\begin{equation}
\label{eq:d_lin}
\bd = \bv_0 + \bmJ_0 \Delta \bvarrho  + \bn.
\end{equation}
Calculating the residual and dropping the reference to a specific fiducial point, we obtain 
\begin{equation}
\label{eq:r_lin}
\br = \bd - \bv = \bmJ \Delta \bvarrho + \bn.
\end{equation}
Moreover,
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix},
\end{equation}
where
\begin{align}
\bN &= \begin{bmatrix} \bO & \bP \end{bmatrix}, & \bM &= \begin{bmatrix} \bQ & \bR \end{bmatrix}, 
\end{align}

\begin{equation}
 [\bO]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \eta_j} = \begin{cases} 
    v_{pq} &\textrm{if}~(p=j)~\textrm{or}~(q=j)\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}

\begin{equation}
 [\bP]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \varphi_j} = \begin{cases}
                                                                        i v_{pq} &\textrm{if}~ p=j\\
                                                                        -i v_{pq} &\textrm{if}~ q=j \\
                                                                        0 & \textrm{otherwise} 
                                                                       \end{cases}
\end{equation}

\begin{equation}
 [\bQ]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} = \begin{cases} 
    v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}

\begin{equation}
 [\bR]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} = \begin{cases} 
    i v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases}.
\end{equation}

The augmented residual is equal to 
\begin{equation}
\breve{\br} = \bJ \Delta \bvarrho + \bn, 
\end{equation}

where $\breve{\br} = [r,\conj{r}]^T$ and 
\begin{equation}
\bJ =
\begin{bmatrix}
 \bmJ\\
 \conj{\bmJ}
\end{bmatrix}.
\end{equation}

STILL NEEDS LOTS OF WORK.

\label{lastpage}

\end{document}

>>>>

\section{LINCAL}
In this section we derive LINCAL \citep{Liu2010} from first principles.
%Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
We can rewrite Eq.~\eqref{eq:vis_red_vec} to
\begin{equation}
\label{eq:lincal_vec}
\bd = \bv(\bvarrho) + \bn, 
\end{equation}
where 
\begin{align}
\left [ \bv(\bvarrho) \right ]_{\alpha_{pq}} &= e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q}\\
&= v_{pq},
\end{align}
and
\begin{equation}
\bvarrho = 
\begin{bmatrix}
\bmath{\eta} \\
\bvarphi \\
\widetilde{\bmath{\eta}} \\
\widetilde{\bvarphi}
\end{bmatrix},\qquad
\begin{aligned}
\bmath{\eta} &= [\eta_1, \eta_2,\cdots \eta_N]^T\\
 \bmath{\varphi} &= [\varphi_1, \varphi_2,\cdots \varphi_N]^T\\
 \widetilde{\bmath{\eta}} &= [\widetilde{\eta_1}, \widetilde{\eta_2},\cdots \widetilde{\eta_L}]^T\\
 \widetilde{\bmath{\varphi}} &= [\widetilde{\varphi_1}, \widetilde{\varphi_2},\cdots \widetilde{\varphi_L}]^T
\end{aligned}.
\label{eq:help}
\end{equation}
Note that the vectors $\bmath{\eta},~\bvarphi,~\widetilde{\bmath{\eta}}$ and $\widetilde{\bvarphi}$ are real valued.

The first order Taylor expansion of Eq.~\eqref{eq:lincal_vec} around the fiducial point $\bvarrho_0$ is equal to
\begin{equation}
\label{eq:d_lin}
\bd = \bv_0 + \bmJ_0 \Delta \bvarrho  + \bn.
\end{equation}
If we calculate the residual, dropping the reference to a specific fiducial point, we obtain: 
\begin{equation}
\label{eq:r_lin}
\br = \bd - \bv = \bmJ \Delta \bvarrho + \bn.
\end{equation}
Moreover,
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix},
\end{equation}
where
\begin{align}
\bN &= \begin{bmatrix} \bO & \bP \end{bmatrix}, & \bM &= \begin{bmatrix} \bQ & \bR \end{bmatrix}, 
\end{align}
\begin{equation}
 [\bO]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \eta_j} = \begin{cases} 
    v_{pq} &\textrm{if}~(p=j)~\textrm{or}~(q=j)\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}
\begin{equation}
 [\bP]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \varphi_j} = \begin{cases}
                                                                        i v_{pq} &\textrm{if}~ p=j\\
                                                                        -i v_{pq} &\textrm{if}~ q=j \\
                                                                        0 & \textrm{otherwise} 
                                                                       \end{cases}
\end{equation}
\begin{equation}
 [\bQ]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} = \begin{cases} 
    v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}
\begin{equation}
 [\bR]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} = \begin{cases} 
    i v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases}.
\end{equation}
Augmenting the residual by taking into account its conjugate results in 
\begin{equation}
\breve{\br} = \bJ \Delta \bvarrho + \bn, 
\end{equation}
where $\breve{\br} = \begin{bmatrix}\br^T & \conj{\br}^T \end{bmatrix}^T$ and 
\begin{equation}
\bJ = 
\begin{bmatrix}
 \bmJ\\  
 \conj{\bmJ}
\end{bmatrix}.
\end{equation}
The solution to 
\begin{equation}
 \min_{\Delta \bvarrho} \| \breve{\br} - \bJ \Delta \bvarrho\|_F^2,
\end{equation}
is equal to 
\begin{equation}
\label{eq:LINCAL_update}
\Delta \bvarrho = (\bJ^H\bJ)^{-1} \bJ^H\breve{\br}. 
\end{equation}
Eq.~\eqref{eq:LINCAL_update} is used to iteratively determine a new estimate of the parameter vector $\bvarrho$ as follows
\begin{equation}
\label{eq:new_rho}
\bvarrho_{k+1} = \bvarrho_k + \Delta \bvarrho_k. 
\end{equation}
Note that we do not explicitly denote the $k$ index in Eq.~\eqref{eq:LINCAL_update}. We update our parameter vector until convergence is reached.   
\label{lastpage}
\end{document}
